Visual proteomics using whole-lamella 2D template matching

### 2022-02-28 manuscript.tex
Merge branch 'main' of https://github.com/jojoelfe/deco_lace_template_matching_manuscript into main [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/31bc357aa966ffec4212bc97259f92b6b7231438.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/31bc357aa966ffec4212bc97259f92b6b7231438/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1913156797

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/0b9b63ca1f5f1f419cc06d1da01657a14abcec8d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@0b9b63c}
on February 25, 2022.

@@

\begin{figure}
\hypertarget{fig:initmatching2}{%
\centering
\includegraphics{figures/initmatching2.pdf}
\caption{This is an example-figurern}\label{fig:initmatching2}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:approach}{%
\centering
\includegraphics{figures/example-figure.pdf}
\caption{This is an example-figurern}\label{fig:approach}
}
\end{figure}

\begin{figure}
\hypertarget{fig:approach2}{%
\centering
\includegraphics{figures/example-figure2.pdf}
\caption{This is an example-figurern}\label{fig:approach2}
}
\end{figure}

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/31bc357aa966ffec4212bc97259f92b6b7231438/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/31bc357aa966ffec4212bc97259f92b6b7231438}{jojoelfe/deco\_lace\_template\_matching\_manuscript@31bc357}
on February 28, 2022.

@@

\begin{figure}
\hypertarget{fig:initmatching2}{%
\centering
\includegraphics{figures/initmatching2.pdf}
\caption{Maximum intensity projection cross-correlation map of micrograph shown in Figure \ref{fig:initmatching}}\label{fig:initmatching2}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:approach}{%
\centering
\includegraphics{figures/approach.pdf}
\caption{DeCo-LACE approach (A) Graphic demonstrating the data-collection strategy for DeCo-LACE}\label{fig:approach}
}
\end{figure}

\begin{figure}
\hypertarget{fig:deco_lace_workflow}{%
\centering
\includegraphics{figures/deco_lace_workflow.pdf}
\caption{Workflow of DeCo-Lace processing}\label{fig:deco_lace_workflow}
}
\end{figure}

\begin{figure}
\hypertarget{fig:lamella_spatial_info}{%
\centering
\includegraphics{figures/lamella_spatial_info.pdf}
\caption{This is an example-figurern}\label{fig:lamella_spatial_info}
}
\end{figure}
